%An in-depth explanation of the problem, including the "business case". What is wrong with the status-quo or what opportunity exists that justifies undertaking this project (expanding upon the problem statement)? If you have a clear customer or sponsor, why do they want you to work on this? What is the existing relationship, if any, between the development team and the customer? This section should occupy 1/2 - 1 full page.

What happens when someone that is hard of hearing is at home and their doorbell is rung? If this person doesn't have any doorbell aids, they won't be able to answer the door and miss whoever is there. There is a large market in developing products and services that will add convenience to peoples lives. There lies an opportunity to create products that would aid people with disabilities such as people that are hard of hearing as well as people who have weak vision. Here at VibeTracked, we aim to create a product that can help people that are hard of hearing by developing a Bluetooth capable wristwatch that will vibrate when the user's doorbell is rung as well as other features. Over many iterations, we hope to add more features to this product that will help the user in more ways than one. 

Our sponsor Dr. Conley, has experience working with projects that directly involve the deaf community throughout his academic career. The relationship between VibeTracked and Dr. Conley stemmed the team members finding out about Dr. Conley through his projects with the deaf community as well as Dr. Gieser recommending him to the team. Dr. Conley decided to become the sponsor to VibeTracked's project after hearing about the team's project and how it involved the deaf community. Through the initial meeting with Dr. Conley and the team members, the two parties have discussed and exchanged various ideas, features, and development paths to take concerning the project. By the end of the development cycle, we hope to have a product that will do many various things that can help enrich the home environment and aid people that are hard of hearing. 