Our system is intended to provide a variety of functions to our customers, such as an alarm system for deaf or hard of hearing people.

Currently, as stated by security.org, the best security alarm system for those who are hard of hearing is ADT Pulse \cite{Vigderman2021}. They professionally install the security system and offer live monitoring. Additionally, they have a phone application that allows for users to interact with the security system and receive alerts via the phone app whenever there’s something that needs attention, and it is possible for strobe lights to be installed for when the alarm goes off \cite{Zions2019}. However, this option is expensive, and it is all done through one’s phone. If someone does not have their phone with them, they will remain unaware to the security risk. With our wrist module however, it is not only affordable, but it can easily remain with you wherever you go and allow you to be immediately notified, even if you set your phone down.

Additionally, our wrist watch allows one to be notified once someone rings a doorbell. Currently, there are a large variety of doorbell receivers for the hearing impaired on the market. A standard example is Hear World Communication's doorbell receiver \cite{HearWorldStrobe}. It retails for around \$100, and once the doorbell is pressed, a loud chime is sounded through one’s home and a strobe light flashes. The main problem with this, however, is that it requires the homeowner to be in the visible range of the strobe light. Installing more strobe lights is an additional cost, and still there may be areas where the lights are not visible. With the wrist module, it allows for the homeowner to be notified of all instances where the door is rung, regardless of where they may be or what may be visible.

Currently, there are devices that use vibration for emergency alerting. For example, there are alarm clocks and fire alarms that vibrate the bed when they go off \cite{WalmartAlarm} \cite{AllegroFire}. However, one is not always near or on there bed, and may require to be notified at some other time.

Another example of emergency vibration are when there are forced text alerts for emergency situations. One study examined the different patterns and found that a variety of deaf or hard of hearing people carried their phone on them for vibration and to be notified of different occurrences where they found that pattern vibration was more effective than constant, and we aim to provide different vibration patterns for our consumers \cite{Harkins2010}.