When you are fascinated by many advantages and add various functions, the parts eventually grow and there is more data to manage. Since Cerberus wristband is basically a "machine" and a complex "information" device at the same time, there are quite a few things to pay attention to. Therefore, even after the product is successfully delivered, we have to manage it to some extent which we have adopted some measures as follows: Data server backup maintenance and Hardware damage support.
%Include a header paragraph specific to your product here. Maintenance and support requirements address items specific to the ongoing maintenance and support of your product after delivery. Think of these requirements as if you were the ones who would be responsible for caring for customers/end user after the product is delivered in its final form and in use "in the field". What would you require to do this job? Specify items such as: where, how and who must be able to maintain the product to correct errors, hardware failures, etc.; required support/troubleshooting manuals/guides; availability/documentation of source code; related technical documentation that must be available for maintainers; specific/unique tools required for maintenance; specific software/environment required for maintenance; etc.

\subsection{Data server backup maintenance}
\subsubsection{Description}
It is essential to make plans and build data backup systems assuming the worst before problems actually arise. Successful data backup systems store large amounts of information using offsite servers or separate drives. Failure to build these systems properly can make data recovery difficult, leading to information loss in the worst-case scenario. In this project, data will be backed up using offsite servers.
\subsubsection{Source}
This requirement meets our team VibeTracked's needs.
\subsubsection{Constraints}
The offsite server crashes do not occur frequently. 
\subsubsection{Standards}
Cloud or Tape storage.
\subsubsection{Priority}
Medium

\subsection{Hardware damage support}
\subsubsection{Description}
When damage occurs to the prototype, it becomes difficult to perform its function. However, it is almost impossible to identify failures due to complex variables such as wiring. If there is an external damage or part problem, we will take measures to replace each part at any time.
\subsubsection{Source}
This requirement meets the customers' needs.
\subsubsection{Constraints}
Must be minor hardware failures.
\subsubsection{Priority}
High